---
title: "Carbon Risk Pricing"
author: "Giulio Fabbri"
date: "2023-05-19"
output: html_document
---

```{r, message=FALSE}
# load packages
library(readxl)
library(tidyverse)
library(AER)
library(dplyr)
library(ggplot2)
library(huxtable)
```


In sustainable finance there are two main hypotesis on how emissions are priced by the stock markets:
- Carbon Greening Hypotesis: Higher emissions mean higher dividends that companies offer to attract investors despite being polluters
- Future greening hypothesis: Higher emissions mean lower dividends because companies tend to keep money for investing in reducing their environmental impact

The main purpose of this project is therefore to provide an elaboration of a large body of public data by showing some simple and intuitive models for investigating these relationships.


## Data load
```{r}
# load dataset
percorso= "C:/Users/Utente/OneDrive/Desktop/esami fatti/sustainable/sustainable.project/Dataset/dataset2.xlsx"
percorso2 = "C:/Users/Utente/OneDrive/Desktop/esami fatti/sus data/dataset_pollution_col.xlsx"

# financial data for each company
data <- read_excel(percorso,sheet = "Financial Data")

# direct and indirect emissions by company
scope1 <- read_excel(percorso, sheet = "Scope1")
scope2 <- read_excel(percorso, sheet = "Scope2")

# polluter-non polluter label for each company 
poll <- read_excel(percorso2, sheet = "Pollution")
```

## Data Preprocessing
```{r}
# change the column names
colnames(data) <- c("company", "metric", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
colnames(scope1) <- c("company", "country", "economic_sector", "sub_industry", "metric", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
colnames(scope2) <- c("company", "metric", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")

# add to data the label polluter or not polluter for each company 
data <- poll %>% left_join(data, by = 'company', multiple = "all")

# find companies with scope1 and scope2 data 
datacommon <- intersect(scope1$company, scope2$company)

# find companies with only complete dataset
data_new <- data[data$company %in% datacommon, ] 
scope1 <- scope1[scope1$company %in% datacommon, ]

#final dataset with complete informations for each company 
df <- scope1[, 1:4] %>% left_join(data_new, by = "company", multiple = "all") 

# extract market measures

div <- df[df$metric == "DIVIDEND PAYOUT PER SHARE", ] %>% filter(!is.na(company))
roe <- df[df$metric == "RETURN ON EQUITY - TOTAL (%)", ] %>% filter(!is.na(company))
mrkt <- df[df$metric == "MRKT VALUE TO BOOK", ] %>% filter(!is.na(company))
tot_ass <- df[df$metric == "TOTAL ASSETS", ] %>% filter(!is.na(company))
roa <- df[df$metric == "RETURN ON ASSETS", ] %>% filter(!is.na(company))
cap_ex <- df[df$metric == "CAPITAL EXPENDT % TOTAL ASSETS", ] %>% filter(!is.na(company))


# WEIGHT
tot_ass <- tot_ass %>% mutate(weight_10 = tot_ass[, '2010']/sum(tot_ass[, '2010']))
tot_ass <- tot_ass %>% mutate(weight_11 = tot_ass[, '2011']/sum(tot_ass[, '2011']))
tot_ass <- tot_ass %>% mutate(weight_12 = tot_ass[, '2012']/sum(tot_ass[, '2012']))
tot_ass <- tot_ass %>% mutate(weight_13 = tot_ass[, '2013']/sum(tot_ass[, '2013']))
tot_ass <- tot_ass %>% mutate(weight_14 = tot_ass[, '2014']/sum(tot_ass[, '2014']))
tot_ass <- tot_ass %>% mutate(weight_15 = tot_ass[, '2015']/sum(tot_ass[, '2015']))
tot_ass <- tot_ass %>% mutate(weight_16 = tot_ass[, '2016']/sum(tot_ass[, '2016']))
tot_ass <- tot_ass %>% mutate(weight_17 = tot_ass[, '2017']/sum(tot_ass[, '2017']))
tot_ass <- tot_ass %>% mutate(weight_18 = tot_ass[, '2018']/sum(tot_ass[, '2018']))
tot_ass <- tot_ass %>% mutate(weight_19 = tot_ass[, '2019']/sum(tot_ass[, '2019']))
tot_ass <- tot_ass %>% mutate(weight_20 = tot_ass[, '2020']/sum(tot_ass[, '2020']))

# WEIGHTED Mean dividends
div <- div %>% mutate(wa_10 = div$'2010' * tot_ass$weight_10$'2010')  
div <- div %>% mutate(wa_11 = div$'2011' * tot_ass$weight_11$'2011')  
div <- div %>% mutate(wa_12 = div$'2012' * tot_ass$weight_12$'2012')  
div <- div %>% mutate(wa_13 = div$'2013' * tot_ass$weight_13$'2013')  
div <- div %>% mutate(wa_14 = div$'2014' * tot_ass$weight_14$'2014')  
div <- div %>% mutate(wa_15 = div$'2015' * tot_ass$weight_15$'2015')  
div <- div %>% mutate(wa_16 = div$'2016' * tot_ass$weight_16$'2016')  
div <- div %>% mutate(wa_17 = div$'2017' * tot_ass$weight_17$'2017')  
div <- div %>% mutate(wa_18 = div$'2018' * tot_ass$weight_18$'2018')  
div <- div %>% mutate(wa_19 = div$'2019' * tot_ass$weight_19$'2019')  
div <- div %>% mutate(wa_20 = div$'2020' * tot_ass$weight_20$'2020')  

div_10 <- div %>% filter(!is.na(wa_10))
div_11 <- div %>% filter(!is.na(wa_11))
div_12 <- div %>% filter(!is.na(wa_12))
div_13 <- div %>% filter(!is.na(wa_13))
div_14 <- div %>% filter(!is.na(wa_14))
div_15 <- div %>% filter(!is.na(wa_15))
div_16 <- div %>% filter(!is.na(wa_16))
div_17 <- div %>% filter(!is.na(wa_17))
div_18 <- div %>% filter(!is.na(wa_18))
div_19 <- div %>% filter(!is.na(wa_19))
div_20 <- div %>% filter(!is.na(wa_20))

div_all <- div[complete.cases(div), ] # 18 observations

year <- c(2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019, 2020)
d_w <- c(mean(div_10$wa_10), mean(div_11$wa_11), mean(div_12$wa_12), mean(div_13$wa_13), mean(div_14$wa_14), mean(div_15$wa_15), 
         mean(div_16$wa_16), mean(div_17$wa_17), mean(div_18$wa_18), mean(div_19$wa_19), mean(div_20$wa_20))
new_dw <- data.frame(year, d_w)
new_dw$year <- factor(new_dw$year,levels = new_dw$year)

```

```{r}

# Weight direct emission of each company for the dimension of the company (for each year)
scope1 <- scope1 %>% mutate(wa_10 = scope1$'2010' * tot_ass$weight_10$'2010')  
scope1 <- scope1 %>% mutate(wa_11 = scope1$'2011' * tot_ass$weight_11$'2011')  
scope1 <- scope1 %>% mutate(wa_12 = scope1$'2012' * tot_ass$weight_12$'2012')  
scope1 <- scope1 %>% mutate(wa_13 = scope1$'2013' * tot_ass$weight_13$'2013')  
scope1 <- scope1 %>% mutate(wa_14 = scope1$'2014' * tot_ass$weight_14$'2014')  
scope1 <- scope1 %>% mutate(wa_15 = scope1$'2015' * tot_ass$weight_15$'2015')  
scope1 <- scope1 %>% mutate(wa_16 = scope1$'2016' * tot_ass$weight_16$'2016')  
scope1 <- scope1 %>% mutate(wa_17 = scope1$'2017' * tot_ass$weight_17$'2017')  
scope1 <- scope1 %>% mutate(wa_18 = scope1$'2018' * tot_ass$weight_18$'2018')  
scope1 <- scope1 %>% mutate(wa_19 = scope1$'2019' * tot_ass$weight_19$'2019')  
scope1 <- scope1 %>% mutate(wa_20 = scope1$'2020' * tot_ass$weight_20$'2020')  

scope1_10 <- scope1 %>% filter(!is.na(wa_10))
scope1_11 <- scope1 %>% filter(!is.na(wa_11))
scope1_12 <- scope1 %>% filter(!is.na(wa_12))
scope1_13 <- scope1 %>% filter(!is.na(wa_13))
scope1_14 <- scope1 %>% filter(!is.na(wa_14))
scope1_15 <- scope1 %>% filter(!is.na(wa_15))
scope1_16 <- scope1 %>% filter(!is.na(wa_16))
scope1_17 <- scope1 %>% filter(!is.na(wa_17))
scope1_18 <- scope1 %>% filter(!is.na(wa_18))
scope1_19 <- scope1 %>% filter(!is.na(wa_19))
scope1_20 <- scope1 %>% filter(!is.na(wa_20))

scope1_all <- scope1[complete.cases(scope1), ] # 18 observations

# weighted emission mean for each year 
year <- c(2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019, 2020)

sc_w <- c(mean(scope1_10$wa_10), mean(scope1_11$wa_11), mean(scope1_12$wa_12), mean(scope1_13$wa_13), mean(scope1_14$wa_14), mean(scope1_15$wa_15), 
         mean(scope1_16$wa_16), mean(scope1_17$wa_17), mean(scope1_18$wa_18), mean(scope1_19$wa_19), mean(scope1_20$wa_20))

new_scw <- data.frame(year, sc_w)
new_scw$year <- factor(new_scw$year,levels = new_scw$year)


# Weight indirect emission of each company for the dimension of the company (for each year)
scope2 <- scope2 %>% mutate(wa_10 = scope2$'2010' * tot_ass$weight_10$'2010')  
scope2 <- scope2 %>% mutate(wa_11 = scope2$'2011' * tot_ass$weight_11$'2011')  
scope2 <- scope2 %>% mutate(wa_12 = scope2$'2012' * tot_ass$weight_12$'2012')  
scope2 <- scope2 %>% mutate(wa_13 = scope2$'2013' * tot_ass$weight_13$'2013')  
scope2 <- scope2 %>% mutate(wa_14 = scope2$'2014' * tot_ass$weight_14$'2014')  
scope2 <- scope2 %>% mutate(wa_15 = scope2$'2015' * tot_ass$weight_15$'2015')  
scope2 <- scope2 %>% mutate(wa_16 = scope2$'2016' * tot_ass$weight_16$'2016')  
scope2 <- scope2 %>% mutate(wa_17 = scope2$'2017' * tot_ass$weight_17$'2017')  
scope2 <- scope2 %>% mutate(wa_18 = scope2$'2018' * tot_ass$weight_18$'2018')  
scope2 <- scope2 %>% mutate(wa_19 = scope2$'2019' * tot_ass$weight_19$'2019')  
scope2 <- scope2 %>% mutate(wa_20 = scope2$'2020' * tot_ass$weight_20$'2020')  

scope2_10 <- scope2 %>% filter(!is.na(wa_10))
scope2_11 <- scope2 %>% filter(!is.na(wa_11))
scope2_12 <- scope2 %>% filter(!is.na(wa_12))
scope2_13 <- scope2 %>% filter(!is.na(wa_13))
scope2_14 <- scope2 %>% filter(!is.na(wa_14))
scope2_15 <- scope2 %>% filter(!is.na(wa_15))
scope2_16 <- scope2 %>% filter(!is.na(wa_16))
scope2_17 <- scope2 %>% filter(!is.na(wa_17))
scope2_18 <- scope2 %>% filter(!is.na(wa_18))
scope2_19 <- scope2 %>% filter(!is.na(wa_19))
scope2_20 <- scope2 %>% filter(!is.na(wa_20))

scope2_all <- scope2[complete.cases(scope2), ] # 18 observations

# weighted emission mean for each year 
year <- c(2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019, 2020)
sc_w2 <- c(mean(scope2_10$wa_10), mean(scope2_11$wa_11), mean(scope2_12$wa_12), mean(scope2_13$wa_13), mean(scope2_14$wa_14), mean(scope2_15$wa_15), 
         mean(scope2_16$wa_16), mean(scope2_17$wa_17), mean(scope2_18$wa_18), mean(scope2_19$wa_19), mean(scope2_20$wa_20))
new_scw2 <- data.frame(year, sc_w2)
new_scw2$year <- factor(new_scw2$year,levels = new_scw2$year)
```

Then we added the economic size information (considered using total assets) for ongi company 

```{r}
# ECONOMIC DIMENSION
tot_ass <- tot_ass %>% mutate(ec_dim_10 = log(tot_ass$'2010'))  
tot_ass <- tot_ass %>% mutate(ec_dim_11 = log(tot_ass$'2011'))
tot_ass <- tot_ass %>% mutate(ec_dim_12 = log(tot_ass$'2012'))
tot_ass <- tot_ass %>% mutate(ec_dim_13 = log(tot_ass$'2013'))
tot_ass <- tot_ass %>% mutate(ec_dim_14 = log(tot_ass$'2014'))
tot_ass <- tot_ass %>% mutate(ec_dim_15 = log(tot_ass$'2015'))
tot_ass <- tot_ass %>% mutate(ec_dim_16 = log(tot_ass$'2016'))
tot_ass <- tot_ass %>% mutate(ec_dim_17 = log(tot_ass$'2017'))
tot_ass <- tot_ass %>% mutate(ec_dim_18 = log(tot_ass$'2018'))
tot_ass <- tot_ass %>% mutate(ec_dim_19 = log(tot_ass$'2019'))
tot_ass <- tot_ass %>% mutate(ec_dim_20 = log(tot_ass$'2020'))

tot_ass$quartile <- cut(tot_ass$ec_dim_10, quantile(tot_ass$ec_dim_10),
                            include.lowest = TRUE, labels = c("Small", "Medium", "Large", "Huge"))

#add quartile and pollution info to the measure datatables
div <- tot_ass[, c(1,40)] %>% left_join(div, by = "company")
scope1 <- tot_ass[, c(1,5,40)] %>% left_join(scope1, by = "company")
scope2 <- scope1[, c(1:6)] %>% left_join(scope2, by = 'company')  
```


## 1 The regression Dividend ~ Scope per year


The first model we tried is of the type:

**dividend_year ~ 0 + scope_year + quartile + economic sector**

This allows us to eliminate the impact of size and economic sector on dividend, for each year (we know these are relevant factors).
We can then use the model to see if there is a significant relationship between emissions and dividends for each year, holding other factors constant 

```{r, warning=FALSE}
# prepare data
reg <- cbind(div[, c(1:6,8:18)], scope1[, c(8:18)], scope2[, c(8:18)]) 

colnames(reg) <- c("company", "quartile", "country", "economic_sector", "sub_industry", "pollution", "d_10", "d_11", "d_12", "d_13", "d_14", "d_15", "d_16", "d_17", "d_18", "d_19", "d_20",
                     "s1_10", "s1_11", "s1_12", "s1_13", "s1_14", "s1_15", "s1_16", "s1_17", "s1_18", "s1_19", "s1_20",
                   "s2_10", "s2_11", "s2_12", "s2_13", "s2_14", "s2_15", "s2_16", "s2_17", "s2_18", "s2_19", "s2_20")

reg$economic_sector <- as.factor(reg$economic_sector)
reg$quartile <- as.factor(reg$quartile)
```


```{r, warning=FALSE}
# remove outliers (boxplot were done in another file)
Upper= 4000000
reg_no_out <- subset(reg, reg[,18:29] < Upper)

```

```{r,warning=FALSE}
#we loose 23 observations checking for outliers
reg_no_out<-reg_no_out[1:40,]
nrow(reg)
nrow(reg_no_out)
```

```{r,warning=FALSE}
# use regr no outliers
reg<-reg_no_out
```

```{r,warning=FALSE}
#regression dividend scope per year
model_10s1= lm(d_10 ~ 0 + s1_10 + quartile+ economic_sector, data = reg)
model_11s1= lm(d_11 ~ 0 + s1_11 + quartile+ economic_sector, data = reg)
model_12s1= lm(d_12 ~ 0 + s1_12 + quartile+ economic_sector, data = reg)
model_13s1= lm(d_13 ~ 0 + s1_13 + quartile+ economic_sector, data = reg)
model_14s1= lm(d_14 ~ 0 + s1_14 + quartile+ economic_sector, data = reg)
model_15s1= lm(d_15 ~ 0 + s1_15 + quartile+ economic_sector, data = reg)
model_16s1= lm(d_16 ~ 0 + s1_16 + quartile+ economic_sector, data = reg)
model_17s1= lm(d_17 ~ 0 + s1_17 + quartile+ economic_sector, data = reg)
model_18s1= lm(d_18 ~ 0 + s1_18 + quartile+ economic_sector, data = reg)
model_19s1= lm(d_19 ~ 0 + s1_19 + quartile+ economic_sector, data = reg)
model_20s1= lm(d_20 ~ 0 + s1_20 + quartile+ economic_sector, data = reg)
```

Scope1 (direct emissions) has no statistically significant effect on dividends,  
now we can try the same method for checking if Scope2 (indirect emissions) have no significant infuence as well.

```{r,warning=FALSE}
library(huxtable)
huxreg(
"2010"=model_10s1,
"2011"=model_11s1,
"2012"=model_12s1,
"2013"=model_13s1,
"2014"=model_14s1,
"2015"=model_15s1,
"2016"=model_16s1,
"2017"=model_17s1,
"2018"=model_18s1,
"2019"=model_19s1,
"2020"=model_20s1)
```




## 2 The regression dividend~scope2 per year

Scope2 (indirect emissions) have no significant infuence as well.

```{r}
#regression dividend scope per year
model_10s2= lm(d_10 ~ 0 + s2_10 + quartile+ economic_sector, data = reg)
model_11s2= lm(d_11 ~ 0 + s2_11 + quartile+ economic_sector, data = reg)
model_12s2= lm(d_12 ~ 0 + s2_12 + quartile+ economic_sector, data = reg)
model_13s2= lm(d_13 ~ 0 + s2_13 + quartile+ economic_sector, data = reg)
model_14s2= lm(d_14 ~ 0 + s2_14 + quartile+ economic_sector, data = reg)
model_15s2= lm(d_15 ~ 0 + s2_15 + quartile+ economic_sector, data = reg)
model_16s2= lm(d_16 ~ 0 + s2_16 + quartile+ economic_sector, data = reg)
model_17s2= lm(d_17 ~ 0 + s2_17 + quartile+ economic_sector, data = reg)
model_18s2= lm(d_18 ~ 0 + s2_18 + quartile+ economic_sector, data = reg)
model_19s2= lm(d_19 ~ 0 + s2_19 + quartile+ economic_sector, data = reg)
model_20s2= lm(d_20 ~ 0 + s2_20 + quartile+ economic_sector, data = reg)
```

```{r}
# scope2 almost 0 effect but significant in 2015-2016
library(huxtable)
huxreg(
"2010"=model_10s2,
"2011"=model_11s2,
"2012"=model_12s2,
"2013"=model_13s2,
"2014"=model_14s2,
"2015"=model_15s2,
"2016"=model_16s2,
"2017"=model_17s2,
"2018"=model_18s2,
"2019"=model_19s2,
"2020"=model_20s2)
```
Scope 2 has no significant effect as well 


## 3 Dividend and scope per sector 2010

We can have a look at the regression of scope over dividend divided by secotr, remembering that we have little data and we cannot generalzie from it 

```{r, warning=FALSE}
#dividend e scope 1
library(ggplot2)
ggplot(reg, aes(s1_10, d_10, color = economic_sector)) +
  geom_point() + 
  geom_smooth(method = lm) +
  labs(x = "Scope 1", y = "Dividend Payout per share") +
  scale_x_continuous(labels = scales::comma) + 
  scale_fill_discrete(name = "Economic Sector") +
  ggtitle("Regression of Scope1 on Dividend Payout (2010)") +
  theme(plot.title = element_text(hjust = 0.5))

```


# 4 REGRESSION (2010 - 2020): TEST the paris agreements effect

To test whether the paris agreement (2015) had an effect in the emission-dividend relationship we can use a model of the type:  

**dividend_year ~ 0 + scope + PA + scope*PA + quartile + economic sector**

this will allow, given the same size and sector, to test the effect of PAris Agreement (PA) on dividends and its interaction with scope (scope*PA)

```{r}
# reshape for regression
reg2 <- div[, -c(7, 19:28)] %>% gather(year, div, -c(1:6)) 
reg3 <- scope1[, -c(7)] %>% gather(year, sp1, -c(1:6))
reg4 <- scope2[, -c(7)] %>% gather(year, sp2, -c(1:6))

merge1 <- reg2[, c(1,8)] %>% left_join(reg3, by = 'company', multiple = "all")  
merge <- reg4[, c(1,8)] %>% left_join(merge1, by = 'company', multiple = "all")
merge <- merge[, c(1,6,7,8,4,5,9,3,10,2)]

# add dummy variable paris agreement
merge <- merge %>% mutate(pa = ifelse(year < '2015', 0, 1))

#add dummy variable scope 1 with respect average
merge <- merge %>% mutate(sp1_less_avg = ifelse(sp1 < mean(sp1), 0,1))

```


```{r, warning=FALSE}
# check outliers
Upper= 4000000
reg_no_out <- subset(reg, reg[,18:29] < Upper)
boxplot(reg_no_out[,18:29], main= "Scope1")
boxplot(reg[,18:29], main= "Scope1 with outliers")
boxplot(reg_no_out[,29:39], main= "Scope2") 
boxplot(reg[,29:39], main= "Scope2 with outliers")
```


```{r}
boxplot(merge$sp1, main= "Scope1 with outliers")
boxplot(merge$sp2, main="Scope2 with outliers")

```

```{r}
Upper1 <- 100000000
Upper2<-20000000
reg_no_out <- subset(merge, merge$sp1 < Upper1 &  merge$sp2< Upper2)

boxplot(reg_no_out$sp1, main= "Scope1")
boxplot(reg_no_out$sp2, main= "Scope2")
```


```{r, results='hide'}
merge_scaled <- merge
scale(merge_scaled[,8:10])
```

```{r error=TRUE}
modello=lm(data= merge, div ~ 0 + sp2+ pa + sp2*pa + economic_sector+ quartile)
huxreg("PA Effect"= modello)
```

## Conclusions for Scope1:
1. Scope1 seems to have a significant negative effect on dividend (99% s.l.), 
against the carbon premium hypothesis.
But the coefficient is so small that this effect have to be classified as 
irrelevant and not meaningful.
2. PA coefficient is significant and negative, indicating that on average dividends have 
decreased after the paris agreement (by little)
3. PA have not influenced the relation dividend-scope1, in fact the Scope*PA effect is not 
significant
─────────────────────────────────────────────────────
                                                                           (1)         
                                                                   ────────────────────
                                    sp1                                    -0.000 ***  
                                                                           (0.000)     
                                    pa                                     -0.349 **   
                                                                           (0.112)     
                                    economic_sectorBasic Materials         49.281 ***  
                                                                           (0.156)     
                                    economic_sectorEnergy                  47.874 ***  
                                                                           (0.166)     
                                    economic_sectorIndustrials             48.859 ***  
                                                                           (0.133)     
                                    economic_sectorTechnology              46.854 ***  
                                                                           (0.166)     
                                    quartileMedium                        -12.996 ***  
                                                                           (0.128)     
                                    quartileLarge                          -7.628 ***  
                                                                           (0.132)     
                                    quartileHuge                           -9.130 ***  
                                                                           (0.134)     
                                    sp1:pa                                  0.000      
                                                                           (0.000)     
                                                                   ────────────────────
                                    N                                  274912          
                                    R2                                      0.749      
                                    logLik                           -1259651.176      
                                    AIC                               2519324.352      
                                  ─────────────────────────────────────────────────────
                                    *** p < 0.001; ** p < 0.01; * p < 0.05.            


## Conclusions for Scope1(same method):
1. Scope2 has a significant positive effect on dividend (99% s.l.),In line the carbon premium hypothesis. But the coefficient is so small (1.416085e-07) hat this effect have to be classified as irrelevant and not meaningful.
2. PA coefficient is not significant
3. PA have not influenced the relation dividend-scope2, in fact the Scope2*PA effect 
is not significant


## Data exploration that was used

These graphs show our sample (which I recall, is not representative of the true European composition, which is beyond our purposes of representing a methodology for investigating these issues)

```{r error=TRUE}

# Analysis of Economic Sector 
ggplot(scope1, aes(x = economic_sector, fill = economic_sector)) + 
  geom_bar(position = position_dodge()) +
  geom_text(stat = 'count', aes(label = after_stat(count)), vjust = -0.30) +
  labs(x = "Economic Sector", y = "Number of observations") + 
  ggtitle("Analysis of Economic Sector (2010 - 2020)") +
  guides(fill = 'none') + 
  theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))  #to center
```


```{r error=TRUE}
# Analysis of Economic Sector across Country
ggplot(scope1, aes(x = country, fill = economic_sector)) + 
  geom_bar(position = position_dodge()) +
  labs(x = "Country", y = "Number of observations") + 
  ggtitle("Analysis of Economic Sector across Country (2010 - 2020)") +
  scale_fill_discrete(name = "Economic Sector") +
  theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))  #to center
```


```{r error=TRUE}
# Analysis of Economic Dimension across Economic Sector
ggplot(tot_ass, aes(x = quartile, fill = economic_sector)) + 
  geom_bar(position = position_dodge()) +
  labs(x = "Quartile", y = "Number of observations") + 
  ggtitle("Analysis of Economic Dimension (2010 - 2020)") +
  scale_fill_discrete(name = "Economic Sector") +
  theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))  #to center
```


```{r error=TRUE}
# Analysis of Economic Dimension across Country
ggplot(tot_ass, aes(x = country, fill = quartile)) + 
  geom_bar(position = position_dodge()) +
  labs(x = "Country", y = "Number of observations") + 
  ggtitle("Analysis of Economic Dimension across Country (2010 - 2020)") +
  scale_fill_discrete(name = "Economic Dimension") +
  theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))  #to center
```


```{r error=TRUE}
# Analysis of Tot Assets across Country
ggplot(tot_ass, aes(x = country, y = '2010', color = economic_sector, size = ec_dim_10)) +
  geom_point(alpha=0.7) + 
  labs(x = 'Country', y = 'Total Assets') + 
  ggtitle("Analysis of Total Assets (2010)") +
  theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))  #to center
```